Flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-05-17 src/tex/ms.tex
[showyourwork] overleaf sync

%It was found with low obliquity, consistent with XXXX~\citep{heitzmann2021obliquity}. Tentative third planet transiting.
%The system's $a/R_*\approx11.7$, eccentricity below .25~\cite{rizzuto2020tess}, so that  
 %\cite{wood2021characterizing} rule out stellar companions for HIP 67522 based on RV, high-resolution imaging, and Gaia data.

@@

Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}) for our analysis, we need to make numerous assumptions. These include the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface. For modulation with the orbital period, we require only that last correlation between footpoint location and orbital phase. Any realistic number of active regions (one or more), a wide range of degrees of differential rotation (from rigid rotator to solar-type), and half-life duration of active regions (day to years) are acceptable, because the observed effect depends predominantly on the visibility of the footpoint, which is governed by orbital motion. The latter is much more stable over long periods of time than the intrinsically dynamic magnetic field configuration. \textcolor{red}{add some references}

@@

\subsection{Intermittency}
\label{sec:discussion:intermittency}
Magnetic star-planet interaction power in a given system may sometimes be low for episodes of time, and high for others. HD 179949 is the prototype example for this phenomenon, wherein the orbital modulation of chromospheric indicators was observable for XXXX out of XXXXX epochs on XXXX years baseline~\citep{shkolnik2003evidence,shkolnik2008nature}. It is not clear how long a continuous epoch of interaction or non-interaction might be. This leaves room for many different explanations. Long-term monitoring is needed to investigate the reasons for the temporary cessation of interaction. Candidate mechanisms for the star include: 
\begin{itemize}
    \item the Alfv\'en radius moving in- and outside the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections;
    \item visibility of the interacting footpoint changing as the magnetic field evolves (more visibility is less modulation with orbital period);
    \item an active latitude moving away from the magnetic footpoints passageway; or
    \item the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
\end{itemize}

If the magnetic field of the planet also changes over time, this might modulate the intensity as well~[e.g.]\citep{turnpenney2018exoplanetinduced}.

The location of active regions within the passageway of the magnetic footpoints may be such that the interaction occurs only when the region faces away from the observer. This could span multiple orbits of the planet, particularly when the surface is populated by few stable active regions, and the orbital and rotational periods are similar. The flip-flop behavior of active longitudes seen in young solar-like stars~(XXXX) could then cause a relatively sudden quenching of interaction by moving the interacting region out of view for a period of time.

>>>>

%It was found with low obliquity, consistent with ~\citep{heitzmann2021obliquity}. Tentative third planet transiting.
%The system's $a/R_*\approx11.7$, eccentricity below .25~\cite{rizzuto2020tess}, so that  
 %\cite{wood2021characterizing} rule out stellar companions for HIP 67522 based on RV, high-resolution imaging, and Gaia data.

@@

Even for the few stars, for which the rotational period is known precisely enough~(see Fig.~\ref{fig:coherence_hist}) for our analysis, we need to make numerous assumptions. These include the number of active regions crossed by the footpoint of interaction, differential rotation, spot evolution, and a significant correlation between the location of the planet and the location of the planet-induced flare on the stellar surface. For modulation with the orbital period, we require only that last correlation between footpoint location and orbital phase. Any realistic number of active regions (one or more), a wide range of degrees of differential rotation (from rigid rotator to solar-type), and half-life duration of active regions (day to years) are acceptable, because the observed effect depends predominantly on the visibility of the footpoint, which is governed by orbital motion. The latter is much more stable over long periods of time than the intrinsically dynamic magnetic field configuration~(see e.g., various works on spot lifetimes in low mass stars~\citealt{giles2017kepler,davenport2015spots, namekata2019lifetimes}).

@@

\subsection{Intermittency}
\label{sec:discussion:intermittency}
Magnetic star-planet interaction power in a given system may sometimes be low for episodes of time, and high for others. HD 179949 is the prototype example for this phenomenon, wherein the orbital modulation of chromospheric indicators was observable for four out of six epochs on a five year baseline~\citep{shkolnik2003evidence,shkolnik2008nature}. It is not clear how long a continuous epoch of interaction or non-interaction might be. This leaves room for many different explanations. Long-term monitoring is needed to investigate the reasons for the temporary cessation of interaction. Candidate mechanisms for the star include: 
\begin{itemize}
    \item the Alfv\'en radius moving in- and outside the planet's orbit, either over the course of an activity cycle, or through short-term variations in the magnetic field and wind properties caused by, e.g., coronal mass ejections;
    \item visibility of the interacting footpoint changing as the magnetic field evolves (more visibility is less modulation with orbital period);
    \item an active latitude moving away from the magnetic footpoints passageway; or
    \item the available magnetic energy decreasing such that the flares or other magnetic interaction indicators still occur but fall below the detection threshold for a period of time.
\end{itemize}

If the magnetic field of the planet also changes over time, this might modulate the intensity as well~\citep[e.g.][]{turnpenney2018exoplanetinduced}.

The location of active regions within the passageway of the magnetic footpoints may be such that the interaction occurs only when the region faces away from the observer. This could span multiple orbits of the planet, particularly when the surface is populated by few stable active regions, and the orbital and rotational periods are similar. The flip-flop behavior of active longitudes seen in young solar-like stars~\citep{berdyugina2005starspots} could then cause a relatively sudden quenching of interaction by moving the interacting region out of view for a period of time.
